What really matters (and to whom): Investigating heterogeneous effects in high-dimensional conjoint analyses

### 2024-12-05 Manuscript files/Manuscript.qmd
updates

![Ext VarImps](figures/RF_VarImps_ext_v3.png){#fig-varimps-ext}

@@

```{r image-panel, echo=FALSE, fig.align='center'}
#| fig-cap: "Exemplary deicision trees for predicting IMCEs based on Covariates."
#| label: fig-imagepanel
library(gridExtra)
library(grid)
library(png)

>>>>

![Ext VarImps](figures/RF_VarImps_ext_v4.png){#fig-varimps-ext}

@@

```{r image-panel, echo=FALSE, fig.align='center', fig.fullwidth=TRUE, out.width="100%"}
#| fig-cap: "Exemplary deicision trees for predicting IMCEs based on Covariates."
#| label: fig-imagepanel
library(gridExtra)
library(grid)
library(png)
